---
title: "Visualize Data"
author: "Jaylin Van Guilder"
format: gfm
execute: 
  echo: true
  eval: true
---

Try your code again
```{r}
#| label: setup1
#| include: false
library(rlang)


```



## Your Turn 0

Add a setup chunk that loads the tidyverse packages.
```{r}
#| label: setup2
#| include: false
library(tidyverse)

```


```{r}
#| label: loading data
head(mpg)
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
#| label: Creating ggplot graph
ggplot(data=mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class)) + 
  labs (x = "Engine Size Displacement",
        y = "Highwasy Mileage (mpg)",
        color = "Class of Vehicle",
        title = "The bigger the engine the less mileage we get on the highway") +
  theme_light()
# Don't need to always put 'mapping =' when doing the code, R will understand.
```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
#| label: ggplot boxplot
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.

```{r}
#| label: ggplot2 Histogram
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy))
```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.

```{r}
#| label: changing bin units
ggplot(data = mpg) +
  geom_histogram(binwidth = 2, mapping = aes(x = hwy))


```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
#| label: Adding color, size, alpha and shape to hist.
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), color = 2, size = 4, alpha = 0.5, shape = 2)
```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
#| label: Difference between facet grid and wrap
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl)
q + facet_grid(drv ~ .)
q + facet_grid(drv ~ cyl)
q + facet_wrap(~ class)
```
> facet_grid forms a matrix of panels defined by row and column whereas facet_wrap wraps a 1d sequence of panels into 2d making a better use of screen space than facet_grid because most displays are mainly rectangular.

## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}
#| label: Bar Chart
ggplot(data = mpg) +
  geom_bar(mapping = aes(x = class, fill = class)) +
  guides(fill = "none") +
  labs(x = "Class of Vehicle",
       y = "Number of Vehicles in Sample") +
  theme_bw()
```

## Quiz

What will this code do?

```{r}
ggplot(mpg, aes(x=displ, y = hwy)) + 
  geom_point(aes(color = class)) +
  geom_smooth(color = "black", 
              se = FALSE,
              method = "lm") 

# ggsave("example.jpg", width = 6, height = 4)
```
> This code will make it easier to see the pattern in the scatterplot, the specific code to show this is the 'geom_smooth()' code.

***

# Take aways

You can use this starter code template to make thousands of graphs with **ggplot2**.

```{r}
#| label: template
#| eval: false
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```